\documentclass{beamer}
\usepackage{etoolbox}\newtoggle{printable}\togglefalse{printable}
\usetheme{Copenhagen}
\usecolortheme{beaver}
\usepackage{listings}
\usepackage{algpseudocode}
\pdfmapfile{+sansmathaccent.map}
\graphicspath{ {Images/} }

\title{Comp240 Market Evaluation \& Business Case}
\author{Alastair Rayner}
\date{\today}

\begin{document}

\maketitle


% ////////////////// TARGET AUDIENCE
\begin{frame}{About the Product}
	The product I have been working on is a lobby system for the BA team Firelock. \pause
	
	This presentation will aim to address whether there is an audience for the game being developed by Firelock, and furthermore which marketing strategy we believe to be the best for this product. \pause
\end{frame}


\begin{frame}{What is the Target Audience for this Product?}		
	\textbf{What is the target audience for this product?} \pause
		\begin{itemize}
			\item One target audience for this product would be people who like to play video games with their friends, especially at LAN parties etc. \pause
			\item Another would be players who like strategy games such as Valkyria Chronicles and Frozen Synapse. \pause
			
				\begin{itemize}
					\item Both of these games have an owner base of around 700,000 players. \pause
					\item Valkyria Chronicles has sold a total of 1.3 million copies according to SteamSpy. \pause
				\end{itemize}	
			\item The demographic for the game would be males and females in the age range of about 12+.  \pause
				\begin{itemize}
					\item This demographic may not have a lot of disposable income, however they may have a lot of spare time. \pause
					\item They may also be interested in merchandise. \pause
				\end{itemize}
			\item The lobby system that I am working on will allow players to play Firelocks game over a local network easily \pause 	
		\end{itemize}
\end{frame}




\end{document}
