% Please do not change the document class
\documentclass{scrartcl}

% Please do not change these packages
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\doublespace

% You may add additional packages here
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{wrapfig}
\graphicspath{ {./images/} }

% Please include a clear, concise, and descriptive title
\title{Portfolio Proposal} 

% Please do not change the subtitle
\subtitle{COMP310 Demake-Proposal}

% Please put your student number in the author field
\author{1507516}

\begin{document}

\maketitle

\abstract{}

\section{Concept}
The concept of my demake is a 2D space shooter, similar to Galaga but based on the modern game Star Citizen.
The game will have a player ship at the bottom of the screen and will be able to fire projectiles at enemies that spawn at the top of the screen.

The player will loose health if hit by projectiles, but if the player kills enemy ships their score will increase.
The aim of the game is to get the best score.

(Stretch)
The player can choose a starting ship, that has different stats, i.e. movement vs health.
Different types of enemies.
The player can have special abilities that they pick up, i.e. chaff, Missiles ect.



\section{Key Mechanic}
The key mechanic of which this demake will be based around firing projectiles at enemy ships and dodging enemies bullets and ships.


\section{Technical Feasibility}
This style of game has been done a few times on legacy game systems, so it should be very feasible.





\end{document}


%The witcher 3
%(the player has 2 swords to combat each enemy)
%(Beasts and humanoids wander around)
%2D top down (zelda style)