% Please do not change the document class
\documentclass{scrartcl}

% Please do not change these packages
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\doublespace

% You may add additional packages here
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{wrapfig}
\graphicspath{ {./images/} }

% Please include a clear, concise, and descriptive title
\title{Undercooked} 

% Please do not change the subtitle
\subtitle{COMP310 Demake-Proposal}

% Please put your student number in the author field
\author{1507516}

\begin{document}

\maketitle

\abstract{}

\section{Concept}
The concept of my demake is a 2D top down cooking game, where the player has to create food as ordered before the time runs out

The game can be co-op as well as single player.

However co-op will be a stretch goal.

The players score will increase with every correctly cooked item served. 
\section{Key Mechanic}
Moving items around a kitchen and doing it as efficiently as possible.

The stretch goals will be to implement co-op and have different levels.

Disasters that happen, such as fire that spawns when food is cooked for too long.
\section{Technical Feasibility}
This type of game is fairly simple, as there is no scrolling backgrounds, and not lots of enemies to render, only the player and the objects that the player can interact with.

The game will have a detailed player sprite, consisting of 4 8x8 sprites, and the tiles will be 8x8 sprites.

The game will have pre-designed levels that the player can walk around in, and interact with certain usable cells, i.e. cooker, chopping board ect.
\end{document}
